Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-09-12 manuscript.Rmd
seperate theme

plots[["Posterior Probability"]] +
  labs(caption = "$p(E|H) = 0.8$, $p(H) = 0.1$",
       y = "$\\mathbb{E}\\big(p(H|E)\\big)$") +
  theme(legend.position = c(.2, .8),
        legend.title = element_blank())
```

@@

plots[!(names(plots) %in% "Posterior Probability")] %>% 
  reduce(`+`) +
  plot_layout(ncol = 2, guides = 'collect') &
  theme_tufte() &
  theme(
    legend.title = element_blank(),
    legend.position = "bottom",
    plot.title = element_text(size = 7),
    axis.text = element_text(size = 6)
  )
```

>>>>

plots[["Posterior Probability"]] +
  labs(caption = "$p(E|H) = 0.8$, $p(H) = 0.1$",
       y = "$\\mathbb{E}\\big(p(H|E)\\big)$") +
  theme_tufte() +
  theme(legend.position = c(.2, .8),
        legend.title = element_blank())
```

@@

plots[!(names(plots) %in% "Posterior Probability")] %>% 
  map(~ . +   theme_tufte()) %>% 
  reduce(`+`) +
  plot_layout(ncol = 2, guides = 'collect') &
  theme_tufte() &
  theme(
    legend.title = element_blank(),
    legend.position = "bottom",
    plot.title = element_text(size = 7),
    axis.text = element_text(size = 6)
  )
```
